%-------------------------
% Resume in Latex
% Author : Saurabh Choudhary
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Saurabh} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 7869473611 ~ \href{mailto:choudharysaurabh412@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{choudharysaurabh412@gmail.com}} ~ 
    \href{https://linkedin.com/in/saurabh-choudhary-379965192/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/saurabh-choudhary}}  ~
    \href{https://github.com/mentalpirate}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/mentalpirate}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shri Shankaracharya Technical Campus}{June. 2018 -- July 2022}
      {Bachelor of Technology in Computer Science and Engineering }{Bhilai, Chhattisgarh}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Skills}
    %\resumeSubHeadingListStart
        \begin{multicols}{3}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Python Programming
                \item Amazon Web Service
                \item API Development (Flask, FastAPI)
                \item Linux Administration
                \item Container orchestration (Docker, Kubernetes)
                \item CI/CD Tools (Github Actions, Jenkins, )

            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Webscoot.io}{August 2022 -- January 2023}
      {Cloud Engineering Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Work profile includes managing Linux servers using automation tools like ansible and involved working with CI/CD,testing and deploying application using Docker, terraform.}
        \resumeItem{Part of the Cloud Engineer Team, responsibilities include working on installation , testing and monitoring of Magento 2 servers , used various tools to ensure resiliency and system reliability.}
        \resumeItem{Collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        \resumeItem{Utilized Github Actions to provide a continuous integration service in order to automate the entire process of Build, Test, Deploy.}
    \resumeItemListEnd
    \resumeSubheading
      {Linux World Pvt Ltd}{June 2021 -- August 2021}
      {Software Engineer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{A training program that cover - Machine learning | Deep learning |OpenCV|Jenkins | Docker | kuberbetes | Git and github | AWS cloud basics | Python | Redhat linux.}
        \resumeItem{Learned about Machine learning different algorithms(Supervised - Unsupervised), and their integration with DevOps tools like Git-GitHub, Docker, Kubernetes, Ansible, Jenkins..}
      \resumeItemListEnd    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{HIGH AVAILABILITY ARCHITECTURE WITH AWS} $|$ \emph{AWS, EC2, ELB Cloud Console}}{}
          \resumeItemListStart
            \resumeItem{Deployed a high available web app on Aws EC2, Aws ELB.}
            \resumeItem{Aws ELB is used for load balancing.}
            \resumeItem{Autoscaling group is used for auto healing and auto scaling the ec2 instances.}
            \resumeItem{Used Cron to schedule the program to execute automatically}
          \resumeItemListEnd % end of itemize for project
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Containerized Application Deployment using Docker} $|$ \emph{Docker, EC2 , DockerHUB}}{}
          \resumeItemListStart
            \resumeItem{Created a Dockerfile using Node as Base Image.}
            \resumeItem{Running container is ec2 instance, configuring security groups, }
            \resumeItem{Pushing build container to private image registry for deployment.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{CI/CD Pipeline using Github Actions} $|$ \emph{Github Actions, node}}{}
          \resumeItemListStart
            \resumeItem{Creating the Github Action Pipelines to automate the process of fetching the files from github..}
            \resumeItem{Creating pipeline for automated building of containers and deploying on AWS infrastructure..}
            \resumeItem{Deploying the container by automating the provision of
infrastructure.}
            \resumeItem{Creating Auth Token for private git repo.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, HTML/CSS, JavaScript, SQL} \\
     \textbf{Developer Tools}{: VS Code, Amazon Web Service, Gitlab} \\
     \textbf{Technologies/Frameworks}{: Linux, Jenkins, GitHub, Flask, FastAPI, WordPress} }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Course / Training}
    \resumeSubHeadingListStart
        \resumeSubheading{Tools and Technology}{}{}{}
            \resumeItemListStart
                \resumeItem{Redhat Certified System Admin Training.}
                \resumeItem{AWS Solution Architect Training.}
                \resumeItem{Devops Training by Kodekloud.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
